---
title: "Manuscript 2: Child Health Outcomes"
author: "Elizabeth Chase"
date: "10/5/2021"
output: pdf_document
---

```{r setup, include=FALSE, echo=FALSE}
library(knitr)
opts_chunk$set(collapse=TRUE, fig.align='center', out.extra = '', fig.pos= "h", tidy=TRUE, tidy.opts=list(blank=TRUE, width.cutoff=40), warning=FALSE,message=FALSE)
options(scipen=999)

rm(list=ls())

library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(logistf)
library(ARTool)
library(lme4)
library(rstanarm)
library(gee)

load("~/Desktop/Research/Jerel Flint/Analyses/child_long.RData")
load("~/Desktop/Research/Jerel Flint/Analyses/adult_data_eliz.RData")

adult_clean_eliz$num_time_notice <- case_when(
  adult_clean_eliz$noticed_water_issue=="1 year *AFTER* it was switched" ~ 12,
  adult_clean_eliz$noticed_water_issue=="2 months *AFTER* it was switched" ~ 2,
  adult_clean_eliz$noticed_water_issue=="Unsure/Don't know" ~ NA_real_,
  adult_clean_eliz$noticed_water_issue=="2 years *AFTER* it was switched" ~ 24,
  adult_clean_eliz$noticed_water_issue=="Less than 1 month *AFTER* the water source was switched" ~ 0.5,
  adult_clean_eliz$noticed_water_issue=="1 month *AFTER* it was switched" ~ 1,
  adult_clean_eliz$noticed_water_issue=="3 months *AFTER* it was switched" ~ 3,
  adult_clean_eliz$noticed_water_issue=="1 year and 2 months *AFTER* it was switched" ~ 14,
  adult_clean_eliz$noticed_water_issue=="6 months *AFTER* it was switched" ~ 6,
  adult_clean_eliz$noticed_water_issue=="9 months *AFTER* it was switched" ~ 9,
  adult_clean_eliz$noticed_water_issue=="1 year and 6 months *AFTER* it was switched" ~ 18,
  adult_clean_eliz$noticed_water_issue=="7 months *AFTER* it was switched" ~ 7,
  adult_clean_eliz$noticed_water_issue=="4 years or more *AFTER* it was switched" ~ 4,
  adult_clean_eliz$noticed_water_issue=="10 months *AFTER* it was switched" ~ 10,
  adult_clean_eliz$noticed_water_issue=="5 months *AFTER* it was switched" ~ 5,
  adult_clean_eliz$noticed_water_issue=="11 months *AFTER* it was switched" ~ 11,
  adult_clean_eliz$noticed_water_issue=="4 months *AFTER* it was switched" ~ 4,
  adult_clean_eliz$noticed_water_issue=="1 year and 5 months *AFTER* it was switched" ~ 17,
  adult_clean_eliz$noticed_water_issue=="8 months *AFTER* it was switched" ~ 8,
  adult_clean_eliz$noticed_water_issue=="3 years *AFTER* it was switched" ~ 36,
  adult_clean_eliz$noticed_water_issue=="2 year and 1 month *AFTER* it was switched" ~ 25,
  adult_clean_eliz$noticed_water_issue=="2 year and 6 months *AFTER* it was switched" ~ 30,
  adult_clean_eliz$noticed_water_issue=="1 year and 3 months *AFTER* it was switched" ~ 15,
  adult_clean_eliz$noticed_water_issue=="1 year and 1 month *AFTER* it was switched" ~ 13
)

adult_clean_eliz$waterlinereplaced <- ifelse(adult_clean_eliz$water_line_status_after_april2014=="My lead/water lines were replaced", 1, ifelse(is.na(adult_clean_eliz$water_line_status_after_april2014), NA_real_, 0))

subadult <- mutate(adult_clean_eliz, parbloodtestf = blood_test_after_april_2014, parbllf = elevated_lead_after_april_2014, parrashesf = rashes_after_april_2014, parhairf = hairloss_after_april_2014, parnausf = nausea_after_april_2014, parirrf = irritable_after_april_2014, parbloodtestc = getscreened, parbllc = elevated_collapse, parrashesc = rash_collapse, parhairc = hair_collapse, parnausc = nausea_collapse, parirrc = irritable_collapse, paroverall = overall_collapse) %>% dplyr::select(inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, water_exaggerated, children_health_harmed, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, ptsdscore, phq, parbloodtestf, parbllf, parrashesf, parhairf, parnausf, parirrf, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children, employ_status, num_time_notice, watertestbinary, current_zip, waterlinereplaced)

child_adult <- left_join(child_final, subadult, by=c("unique_id"))

rm(list=c("adult_clean_eliz", "subadult", "child_final"))

samp1 <- nrow(child_adult)

child_adult <- filter(child_adult, age.x >= 0.5)
samp2 <- nrow(child_adult)

child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$blood_test_after_april_2014), NA_real_, 0))

child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014), NA_real_, 0))

child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$rash_after_april_2014), NA_real_, 0))

child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hairloss_after_april_2014), NA_real_, 0))

child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$learning_after_april_2014), NA_real_, 0))

child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hyper_after_april_2014), NA_real_, 0))

child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$irritable_after_april_2014), NA_real_, 0))

child_adult$watersource2 <- ifelse(child_adult$watersource=="Bottled water", 1, ifelse(is.na(child_adult$watersource), NA_real_, 0))

child_adult$employ_status2 <- ifelse(child_adult$employ_status=="Employed", "Employed", ifelse(child_adult$employ_status=="Unemployed", "Unemployed", ifelse(is.na(child_adult$employ_status), NA_character_, "Other")))

symp_sub <- dplyr::select(child_adult, gettested, elevbll, rash, hair, learn, hyper, irritable)

child_adult$overall_symp <- rowSums(symp_sub, na.rm=TRUE)

child_adult$racecollapse <- case_when(
  child_adult$reth=="Black or African American" ~ "Black",
  child_adult$reth=="Latino or Hispanic" | child_adult$reth=="Middle Eastern" | child_adult$reth=="Mixed Race" ~ "Other",
  child_adult$reth=="White" ~ "White"
)

exam <- dplyr::select(child_adult, child, unique_id, relationship, age.x, gender.x, public_benefits, gettested, elevbll, rash, hair, learn, hyper, irritable, overall_symp, racecollapse, blood_test_after_april_2014, water_exaggerated)

child_adult2 <- child_adult[complete.cases(exam)]
child_adult <- child_adult2
```

## Descriptives

Initially, our data consisted of `r samp1` children. I then impose our first inclusion criterion: children age 6 months and up. This takes the sample down to `r samp2` children. Then I restrict to children with complete data for all predictors used in modeling. This results in a sample of `r nrow(child_adult)` children.

Here are some descriptives on these children:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
child_adult$relationship <- factor(child_adult$relationship, levels=c("Your child", "Your grandchild", "Your sister or stepsister", "Your brother or stepbrother", "Your niece or nephew", "Your friend's or acquaintance's child or relative", "Other relationship"), ordered = TRUE)
child_adult$watersource2 <- factor(child_adult$watersource2, levels=c(0, 1), labels=c("Non-bottled water", "Bottled water"))
child_adult$gettested <- factor(child_adult$gettested, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$elevbll <- factor(child_adult$elevbll, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$rash <- factor(child_adult$rash, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$hair <- factor(child_adult$hair, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$learn <- factor(child_adult$learn, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$hyper <- factor(child_adult$hyper, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$irritable <- factor(child_adult$irritable, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$gendercollapse <- ifelse(child_adult$gender.y=="Transgender Woman" | child_adult$gender.y=="Female", "Female", ifelse(is.na(child_adult$gender.y), NA_character_, "Male"))

var_label(child_adult$relationship) <- "Child's relationship to survey respondent"
var_label(child_adult$age.x) <- "Child age"
var_label(child_adult$gender.x) <- "Child gender"
var_label(child_adult$watersource2) <- "Child water source"
var_label(child_adult$gettested) <- "Blood lead test after April 2014"
var_label(child_adult$elevbll) <- "Elevated BLLs after April 2014"
var_label(child_adult$rash) <- "Rashes after April 2014"
var_label(child_adult$hair) <- "Hair loss after April 2014"
var_label(child_adult$learn) <- "Learning delays after April 2014"
var_label(child_adult$hyper) <- "Hyperactivity after April 2014"
var_label(child_adult$irritable) <- "Irritability after April 2014"
var_label(child_adult$overall_symp) <- "Total number of symptoms after April 2014"
var_label(child_adult$gendercollapse) <- "Guardian's gender"
var_label(child_adult$collapserace) <- "Guardian's race/ethnicity"
var_label(child_adult$collapseeduc) <- "Guardian's education"
var_label(child_adult$public_benefits) <- "Guardian receives public benefits"
var_label(child_adult$confidants2) <- "Guardian's social network size"
var_label(child_adult$age.y) <- "Guardian's age"
var_label(child_adult$employ_status2) <- "Guardian's employment status"

child_adult$racecollapse <- factor(child_adult$racecollapse)
child_adult$unique_id <- factor(child_adult$unique_id)

child_adult$racecollapse2 <- case_when(
  child_adult$racecollapse=="Black" ~ "Black",
  child_adult$racecollapse=="White" | child_adult$racecollapse=="Other" ~ "White/Other",
  is.na(child_adult$racecollapse) ~ NA_character_
)

child_adult$racecollapse2 <- factor(child_adult$racecollapse2)

child_adult <- arrange(child_adult, unique_id, racecollapse, racecollapse2)

m <- art(relationship ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- data.frame("Outcome" = "Relationship", "Pvalue" = anova(m)$`Pr(>F)`)
m <- art(age.x ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- rbind(pvalues, data.frame("Outcome" = "Child age", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(gender.x, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- rbind(pvalues, data.frame("Outcome" = "Gender", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(watersource2, ordered=TRUE) ~ racecollapse2 + (1 | unique_id), data=child_adult[!is.na(child_adult$watersource2),])
#pvalues <- rbind(pvalues, data.frame("Outcome" = "Watersource", "Pvalue" = anova(m)$`Pr(>F)`))
pvalues <- rbind(pvalues, data.frame("Outcome" = "Watersource", "Pvalue" = NA_real_))
m <- art(factor(gettested, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$gettested),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "BloodTest", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(elevbll, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$elevbll),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "BLLs", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(rash, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$rash),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Rash", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(hair, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$hair),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Hairloss", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(learn, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$learn),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Learning", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(hyper, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$hyper),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Hyper", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(irritable, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$irritable),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Irritable", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(overall_symp ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- rbind(pvalues, data.frame("Outcome" = "Overall", "Pvalue" = anova(m)$`Pr(>F)`))
child_adult$age_grp <- case_when(
  child_adult$age.y < 30 ~ "20-29",
  child_adult$age.y >= 30 & child_adult$age.y < 40 ~ "30-39",
  child_adult$age.y >= 40 & child_adult$age.y < 40 ~ "40-49",
  child_adult$age.y >= 50 ~ "50-73"
)
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(age_grp, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$age_grp),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian age", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(gendercollapse, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$gender.y),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's Gender", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(collapserace, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$collapserace),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's Race", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(collapseeduc, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$collapseeduc),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's Education", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(public_benefits, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$public_benefits),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian receives public benefits", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(employ_status2, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$employ_status2),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's employment status", "Pvalue" = anova(m)$`Pr(>F)`))

child_adult$agegrp2 <- case_when(
  child_adult$age.x <= 0.5 ~ "Infant",
  child_adult$age.x > 0.5 ~ "Child"
)

table_pred <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status2"), strata = "racecollapse", data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_pred_nostrat <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status2"), data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_outcome <- CreateTableOne(vars=c("gettested", "elevbll", "rash", "hair", "learn", "hyper","irritable", "overall_symp"), strata = "racecollapse", data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_outcome_nostrat <- CreateTableOne(vars=c("gettested", "elevbll", "rash", "hair", "learn", "hyper","irritable", "overall_symp"), data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

test <- print(table_pred, contDigits=1, varLabel = T, printToggle=FALSE)
test["Child's relationship to survey respondent (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Relationship", 2], digits = 3))
test["Child age (mean (SD))", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Child age", 2], digits = 3))
test["Child gender = Male (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Gender", 2], digits = 3))
test["Guardian's age (mean (SD))", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian age", 2], digits = 3))
test["Guardian's gender = Male (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's Gender", 2], digits = 3))
test["Guardian's race/ethnicity (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's Race", 2], digits = 3))
test["Guardian's education (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's Education", 2], digits = 3))
test["Guardian receives public benefits (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian receives public benefits", 2], digits = 3))
test["Guardian's employment status (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's employment status", 2], digits = 3))

test2 <- print(table_outcome, contDigits=1, varLabel = T, printToggle=FALSE)
test2["Blood lead test after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="BloodTest", 2], digits = 3))
test2["Elevated BLLs after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="BLLs", 2], digits = 3))
test2["Rashes after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Rash", 2], digits = 3))
test2["Hair loss after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Hairloss", 2], digits = 3))
test2["Learning delays after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Learning", 2], digits = 3))
test2["Hyperactivity after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Hyper", 2], digits = 3))
test2["Irritability after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Irritable", 2], digits = 3))
test2["Total number of symptoms after April 2014 (mean (SD))", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Overall", 2], digits = 3))

kable(test, booktabs=T) %>% add_indent(c(3:9, 15:17, 19:23, 25:27, 29:31)) %>% kable_styling(position="center")

kable(print(table_pred_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:9, 15:17, 19:23, 25:27, 29:31)) %>% kable_styling(position="center")

kable(test2, booktabs=T) %>% kable_styling(position="center")

kable(print(table_outcome_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% kable_styling(position="center")
```

\newpage

## Multivariable modeling results (GEE)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#For water source:
child_adult$water_exaggeratedbinary <- as.numeric(child_adult$water_exaggerated=="Agree" | child_adult$water_exaggerated=="Strongly Agree")
child_adult$pubben <- ifelse(child_adult$public_benefits=="Yes", 1, ifelse(is.na(child_adult$public_benefits), NA_real_, 0))
child_adult$bottledwater <- ifelse(child_adult$watersource=="Bottled water", 1, ifelse(is.na(child_adult$watersource), NA_real_, 0))
child_adult$employcollapse <- ifelse(child_adult$employ_status=="Employed", "Employed", ifelse(child_adult$employ_status=="Unemployed", "Unemployed", ifelse(is.na(child_adult$employ_status), NA_character_, "Other")))

child_adult <- arrange(child_adult, unique_id)

#For getting tested:
tested_model <- gee((as.numeric(gettested)-1) ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable") 

mysum <- summary(tested_model)$coefficients

mysum

effects_mat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 1], "SE" = mysum[2:7, 4])

#For having elevated BLLs (restricting to children who were screened):
bll_model <- gee((as.numeric(elevbll)-1) ~ gender.x + age.x + racecollapse + pubben, id = unique_id, data = child_adult[child_adult$gettested=="Yes",], family = "binomial", corstr = "exchangeable") 

mysum <- summary(bll_model)$coefficients

mysum

subdat <- data.frame("Outcome" = rep("Elevated BLLs", 5), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)"), "Estimate" = mysum[2:6, 1], "SE" = mysum[2:6, 4])

effects_mat <- rbind(effects_mat, subdat)

#For having rashes:
rash_model <- gee((as.numeric(rash)-1) ~ gender.x + age.x + racecollapse + pubben + gettested  + elevbll, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable") 

mysum <- summary(rash_model)$coefficients

mysum

subdat <- data.frame("Outcome" = rep("Rashes", 7), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:8, 1], "SE" = mysum[2:8, 4])

effects_mat <- rbind(effects_mat, subdat)

#For having learning delays:
learn_model <- gee((as.numeric(learn)-1) ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable") 

mysum <- summary(learn_model)$coefficients

mysum

subdat <- data.frame("Outcome" = rep("Learning delays", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 1], "SE" = mysum[2:9, 4])

effects_mat <- rbind(effects_mat, subdat)

#For having hyperactivity:
hyper_model <- gee((as.numeric(hyper)-1) ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable") 

mysum <- summary(hyper_model)$coefficients

mysum

subdat <- data.frame("Outcome" = rep("Hyperactivity", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 1], "SE" = mysum[2:9, 4])

effects_mat <- rbind(effects_mat, subdat)

#For having irritability:
irr_model <- gee((as.numeric(irritable)-1) ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable") 

mysum <- summary(irr_model)$coefficients

mysum

subdat <- data.frame("Outcome" = rep("Irritability", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 1], "SE" = mysum[2:9, 4])

effects_mat <- rbind(effects_mat, subdat)

#For overall symptoms:
overall_model <- gee(overall_symp ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll, id = unique_id, data = child_adult, family = "poisson", corstr = "exchangeable") 
mysum <- summary(overall_model)$coefficients

mysum

subdat <- data.frame("Outcome" = rep("Total Symptoms", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 1], "SE" = mysum[2:9, 4])

effects_mat <- rbind(effects_mat, subdat)
```

Adjusting for multiple testing:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
effects_mat$Lower <- exp(effects_mat$Estimate - 1.96*effects_mat$SE)
effects_mat$Upper <- exp(effects_mat$Estimate + 1.96*effects_mat$SE)
effects_mat$OR <- exp(effects_mat$Estimate)
effects_mat$pvalue <- pnorm(abs(effects_mat$Estimate/effects_mat$SE), lower.tail = FALSE)
effects_mat$BHPvalue <- p.adjust(effects_mat$pvalue, method="BH")

effects_mat$prettyp <- round(effects_mat$pvalue, digits = 2)
effects_mat$prettypBH <- round(effects_mat$BHPvalue, digits = 2)
effects_mat$sig <- effects_mat$pvalue < 0.05

effects_mat$label <- paste0(round(effects_mat$OR, digits=1), " (", round(effects_mat$Lower, digits = 1), ", ", round(effects_mat$Upper, digits = 1), ")")

pretty_effects <- dplyr::select(effects_mat, Outcome, Variable, label, prettypBH)
rownames(pretty_effects) <- NULL

kable(pretty_effects)
```
