---
title: "Manuscript 2: Child Health Outcomes"
author: "Elizabeth Chase"
date: "10/5/2021"
output: pdf_document
---

```{r setup, include=FALSE, echo=FALSE}
library(knitr)
opts_chunk$set(collapse=TRUE, fig.align='center', out.extra = '', fig.pos= "h", tidy=TRUE, tidy.opts=list(blank=TRUE, width.cutoff=40), warning=FALSE,message=FALSE)
options(scipen=999)

rm(list=ls())

library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(logistf)
library(ARTool)
library(lme4)
library(rstanarm)

load("~/Desktop/Research/Jerel Flint/Analyses/child_long.RData")
load("~/Desktop/Research/Jerel Flint/Analyses/adult_data_eliz.RData")

adult_clean_eliz$num_time_notice <- case_when(
  adult_clean_eliz$noticed_water_issue=="1 year *AFTER* it was switched" ~ 12,
  adult_clean_eliz$noticed_water_issue=="2 months *AFTER* it was switched" ~ 2,
  adult_clean_eliz$noticed_water_issue=="Unsure/Don't know" ~ NA_real_,
  adult_clean_eliz$noticed_water_issue=="2 years *AFTER* it was switched" ~ 24,
  adult_clean_eliz$noticed_water_issue=="Less than 1 month *AFTER* the water source was switched" ~ 0.5,
  adult_clean_eliz$noticed_water_issue=="1 month *AFTER* it was switched" ~ 1,
  adult_clean_eliz$noticed_water_issue=="3 months *AFTER* it was switched" ~ 3,
  adult_clean_eliz$noticed_water_issue=="1 year and 2 months *AFTER* it was switched" ~ 14,
  adult_clean_eliz$noticed_water_issue=="6 months *AFTER* it was switched" ~ 6,
  adult_clean_eliz$noticed_water_issue=="9 months *AFTER* it was switched" ~ 9,
  adult_clean_eliz$noticed_water_issue=="1 year and 6 months *AFTER* it was switched" ~ 18,
  adult_clean_eliz$noticed_water_issue=="7 months *AFTER* it was switched" ~ 7,
  adult_clean_eliz$noticed_water_issue=="4 years or more *AFTER* it was switched" ~ 4,
  adult_clean_eliz$noticed_water_issue=="10 months *AFTER* it was switched" ~ 10,
  adult_clean_eliz$noticed_water_issue=="5 months *AFTER* it was switched" ~ 5,
  adult_clean_eliz$noticed_water_issue=="11 months *AFTER* it was switched" ~ 11,
  adult_clean_eliz$noticed_water_issue=="4 months *AFTER* it was switched" ~ 4,
  adult_clean_eliz$noticed_water_issue=="1 year and 5 months *AFTER* it was switched" ~ 17,
  adult_clean_eliz$noticed_water_issue=="8 months *AFTER* it was switched" ~ 8,
  adult_clean_eliz$noticed_water_issue=="3 years *AFTER* it was switched" ~ 36,
  adult_clean_eliz$noticed_water_issue=="2 year and 1 month *AFTER* it was switched" ~ 25,
  adult_clean_eliz$noticed_water_issue=="2 year and 6 months *AFTER* it was switched" ~ 30,
  adult_clean_eliz$noticed_water_issue=="1 year and 3 months *AFTER* it was switched" ~ 15,
  adult_clean_eliz$noticed_water_issue=="1 year and 1 month *AFTER* it was switched" ~ 13
)

adult_clean_eliz$waterlinereplaced <- ifelse(adult_clean_eliz$water_line_status_after_april2014=="My lead/water lines were replaced", 1, ifelse(is.na(adult_clean_eliz$water_line_status_after_april2014), NA_real_, 0))

subadult <- mutate(adult_clean_eliz, parbloodtestf = blood_test_after_april_2014, parbllf = elevated_lead_after_april_2014, parrashesf = rashes_after_april_2014, parhairf = hairloss_after_april_2014, parnausf = nausea_after_april_2014, parirrf = irritable_after_april_2014, parbloodtestc = getscreened, parbllc = elevated_collapse, parrashesc = rash_collapse, parhairc = hair_collapse, parnausc = nausea_collapse, parirrc = irritable_collapse, paroverall = overall_collapse) %>% dplyr::select(inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, water_exaggerated, children_health_harmed, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, ptsdscore, phq, parbloodtestf, parbllf, parrashesf, parhairf, parnausf, parirrf, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children, employ_status, num_time_notice, watertestbinary, current_zip, waterlinereplaced)

child_adult <- left_join(child_final, subadult, by=c("unique_id"))

rm(list=c("adult_clean_eliz", "subadult", "child_final"))

samp1 <- nrow(child_adult)

#child_adult <- filter(child_adult, age.x >= 5)
child_adult <- filter(child_adult, age.x >= 0.5)
samp2 <- nrow(child_adult)

##child_adult <- filter(child_adult, relationship == "Your child" | relationship == "Your grandchild")

child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$blood_test_after_april_2014), NA_real_, 0))

child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014), NA_real_, 0))

child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$rash_after_april_2014), NA_real_, 0))

child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hairloss_after_april_2014), NA_real_, 0))

child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$learning_after_april_2014), NA_real_, 0))

child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hyper_after_april_2014), NA_real_, 0))

child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$irritable_after_april_2014), NA_real_, 0))

child_adult$watersource2 <- ifelse(child_adult$watersource=="Bottled water", 1, ifelse(is.na(child_adult$watersource), NA_real_, 0))

child_adult$employ_status2 <- ifelse(child_adult$employ_status=="Employed", "Employed", ifelse(child_adult$employ_status=="Unemployed", "Unemployed", ifelse(is.na(child_adult$employ_status), NA_character_, "Other")))

symp_sub <- dplyr::select(child_adult, gettested, elevbll, rash, hair, learn, hyper, irritable)

child_adult$overall_symp <- rowSums(symp_sub, na.rm=TRUE)

child_adult$racecollapse <- case_when(
  child_adult$reth=="Black or African American" ~ "Black",
  child_adult$reth=="Latino or Hispanic" | child_adult$reth=="Middle Eastern" | child_adult$reth=="Mixed Race" ~ "Other",
  child_adult$reth=="White" ~ "White"
)

exam <- dplyr::select(child_adult, child, unique_id, relationship, age.x, gender.x, public_benefits, gettested, elevbll, rash, hair, learn, hyper, irritable, overall_symp, racecollapse, blood_test_after_april_2014, water_exaggerated)

child_adult2 <- child_adult[complete.cases(exam)]
child_adult <- child_adult2
```

## Introductory Remarks

Note: May 2021 

This report was an attempt to respond to two key reviewer concerns: 1) the presence of children under age 5 in our data--and thus not alive in April 2014, when the water switch happened, and 2) what to do with children who were described by a caregiver who wasn't their parent or grandparent. 

I tried a number of things to figure out what to do with children under age 5. Part of the problem here is that we were looking at excess mortality outcomes (i.e. "Did the child have this symptom after but not before April 2014?"), and for children under age 5, this wasn't defined, since the child wasn't alive before April 2014. I considered looking at 1) just the after outcome ("Did the child have this symptom after April 2014, regardless of whether they had it before 2014?") or 2) forcibly assuming that children under age 5 didn't have the symptom before April 2014. I was disturbed that these two outcome definitions resulted in  different results, with outcome definition (2) yielding many significant results, while outcome definition (1) yielded almost no significant results and different directions of association. That's bad news. Initially, I thought we would exclude all children under age 5. However, after more discussions with Jerel, we instead decided to restrict to children ages 6 months and up, and use outcome definition (1).  

I then looked a little more closely at the second inclusion criteria: children described by an aunt/uncle/babysitter/sibling, rather than a parent/grandparent. After investigating these children more closely, I concluded that we should keep them. They aren't significantly different from children described by a parent/grandparent, and including them in the sample doesn't affect the direction/magnitude of any associations, but it *does* increase our sample size enough to start seeing significant findings, because the larger sample size shrinks the standard errors.

Therefore, I have concluded that our inclusion criteria will be children ages 6 months and up, considering outcomes based on just after April 2014 (and not before) described by any caregiver living in the City of Flint. 

Note: Oct. 2021

This analysis was redone using Bayesian models, in order to meet a reviewer request for models that would not converge using REML. This allows us to address the issues with small sample size and separation in the data.

\newpage

## Descriptives

Initially, our data consisted of `r samp1` children. I then impose our first inclusion criterion: children age 6 months and up. This takes the sample down to `r samp2` children. Then I restrict to children with complete data for all predictors used in modeling. This results in a sample of `r nrow(child_adult)` children.

Here are some descriptives on these children:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
child_adult$relationship <- factor(child_adult$relationship, levels=c("Your child", "Your grandchild", "Your sister or stepsister", "Your brother or stepbrother", "Your niece or nephew", "Your friend's or acquaintance's child or relative", "Other relationship"), ordered = TRUE)
child_adult$watersource2 <- factor(child_adult$watersource2, levels=c(0, 1), labels=c("Non-bottled water", "Bottled water"))
child_adult$gettested <- factor(child_adult$gettested, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$elevbll <- factor(child_adult$elevbll, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$rash <- factor(child_adult$rash, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$hair <- factor(child_adult$hair, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$learn <- factor(child_adult$learn, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$hyper <- factor(child_adult$hyper, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$irritable <- factor(child_adult$irritable, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$gendercollapse <- ifelse(child_adult$gender.y=="Transgender Woman" | child_adult$gender.y=="Female", "Female", ifelse(is.na(child_adult$gender.y), NA_character_, "Male"))

var_label(child_adult$relationship) <- "Child's relationship to survey respondent"
var_label(child_adult$age.x) <- "Child age"
var_label(child_adult$gender.x) <- "Child gender"
var_label(child_adult$watersource2) <- "Child water source"
var_label(child_adult$gettested) <- "Blood lead test after April 2014"
var_label(child_adult$elevbll) <- "Elevated BLLs after April 2014"
var_label(child_adult$rash) <- "Rashes after April 2014"
var_label(child_adult$hair) <- "Hair loss after April 2014"
var_label(child_adult$learn) <- "Learning delays after April 2014"
var_label(child_adult$hyper) <- "Hyperactivity after April 2014"
var_label(child_adult$irritable) <- "Irritability after April 2014"
var_label(child_adult$overall_symp) <- "Total number of symptoms after April 2014"
var_label(child_adult$gendercollapse) <- "Guardian's gender"
var_label(child_adult$collapserace) <- "Guardian's race/ethnicity"
var_label(child_adult$collapseeduc) <- "Guardian's education"
var_label(child_adult$public_benefits) <- "Guardian receives public benefits"
var_label(child_adult$confidants2) <- "Guardian's social network size"
var_label(child_adult$age.y) <- "Guardian's age"
var_label(child_adult$employ_status2) <- "Guardian's employment status"

child_adult$racecollapse <- factor(child_adult$racecollapse)
child_adult$unique_id <- factor(child_adult$unique_id)

child_adult$racecollapse2 <- case_when(
  child_adult$racecollapse=="Black" ~ "Black",
  child_adult$racecollapse=="White" | child_adult$racecollapse=="Other" ~ "White/Other",
  is.na(child_adult$racecollapse) ~ NA_character_
)

child_adult$racecollapse2 <- factor(child_adult$racecollapse2)

child_adult <- arrange(child_adult, unique_id, racecollapse, racecollapse2)

m <- art(relationship ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- data.frame("Outcome" = "Relationship", "Pvalue" = anova(m)$`Pr(>F)`)
m <- art(age.x ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- rbind(pvalues, data.frame("Outcome" = "Child age", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(gender.x, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- rbind(pvalues, data.frame("Outcome" = "Gender", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(watersource2, ordered=TRUE) ~ racecollapse2 + (1 | unique_id), data=child_adult[!is.na(child_adult$watersource2),])
#pvalues <- rbind(pvalues, data.frame("Outcome" = "Watersource", "Pvalue" = anova(m)$`Pr(>F)`))
pvalues <- rbind(pvalues, data.frame("Outcome" = "Watersource", "Pvalue" = NA_real_))
m <- art(factor(gettested, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$gettested),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "BloodTest", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(elevbll, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$elevbll),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "BLLs", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(rash, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$rash),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Rash", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(hair, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$hair),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Hairloss", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(learn, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$learn),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Learning", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(hyper, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$hyper),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Hyper", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(irritable, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$irritable),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Irritable", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(overall_symp ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- rbind(pvalues, data.frame("Outcome" = "Overall", "Pvalue" = anova(m)$`Pr(>F)`))
child_adult$age_grp <- case_when(
  child_adult$age.y < 30 ~ "20-29",
  child_adult$age.y >= 30 & child_adult$age.y < 40 ~ "30-39",
  child_adult$age.y >= 40 & child_adult$age.y < 40 ~ "40-49",
  child_adult$age.y >= 50 ~ "50-73"
)
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(age_grp, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$age_grp),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian age", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(gendercollapse, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$gender.y),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's Gender", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(collapserace, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$collapserace),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's Race", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(collapseeduc, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$collapseeduc),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's Education", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(public_benefits, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$public_benefits),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian receives public benefits", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(employ_status2, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$employ_status2),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's employment status", "Pvalue" = anova(m)$`Pr(>F)`))

child_adult$agegrp2 <- case_when(
  child_adult$age.x <= 0.5 ~ "Infant",
  child_adult$age.x > 0.5 ~ "Child"
)

table_pred <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status2"), strata = "racecollapse", data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_pred_nostrat <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status2"), data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_outcome <- CreateTableOne(vars=c("gettested", "elevbll", "rash", "hair", "learn", "hyper","irritable", "overall_symp"), strata = "racecollapse", data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_outcome_nostrat <- CreateTableOne(vars=c("gettested", "elevbll", "rash", "hair", "learn", "hyper","irritable", "overall_symp"), data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

test <- print(table_pred, contDigits=1, varLabel = T, printToggle=FALSE)
test["Child's relationship to survey respondent (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Relationship", 2], digits = 3))
test["Child age (mean (SD))", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Child age", 2], digits = 3))
test["Child gender = Male (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Gender", 2], digits = 3))
test["Guardian's age (mean (SD))", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian age", 2], digits = 3))
test["Guardian's gender = Male (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's Gender", 2], digits = 3))
test["Guardian's race/ethnicity (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's Race", 2], digits = 3))
test["Guardian's education (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's Education", 2], digits = 3))
test["Guardian receives public benefits (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian receives public benefits", 2], digits = 3))
test["Guardian's employment status (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's employment status", 2], digits = 3))

test2 <- print(table_outcome, contDigits=1, varLabel = T, printToggle=FALSE)
test2["Blood lead test after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="BloodTest", 2], digits = 3))
test2["Elevated BLLs after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="BLLs", 2], digits = 3))
test2["Rashes after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Rash", 2], digits = 3))
test2["Hair loss after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Hairloss", 2], digits = 3))
test2["Learning delays after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Learning", 2], digits = 3))
test2["Hyperactivity after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Hyper", 2], digits = 3))
test2["Irritability after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Irritable", 2], digits = 3))
test2["Total number of symptoms after April 2014 (mean (SD))", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Overall", 2], digits = 3))

kable(test, booktabs=T) %>% add_indent(c(3:9, 15:17, 19:23, 25:27, 29:31)) %>% kable_styling(position="center")

kable(print(table_pred_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:9, 15:17, 19:23, 25:27, 29:31)) %>% kable_styling(position="center")

kable(test2, booktabs=T) %>% kable_styling(position="center")

kable(print(table_outcome_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% kable_styling(position="center")
```

\newpage

## Multivariable modeling results (normal priors)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#For water source:
child_adult$water_exaggeratedbinary <- as.numeric(child_adult$water_exaggerated=="Agree" | child_adult$water_exaggerated=="Strongly Agree")
child_adult$pubben <- ifelse(child_adult$public_benefits=="Yes", 1, ifelse(is.na(child_adult$public_benefits), NA_real_, 0))
child_adult$bottledwater <- ifelse(child_adult$watersource=="Bottled water", 1, ifelse(is.na(child_adult$watersource), NA_real_, 0))
child_adult$employcollapse <- ifelse(child_adult$employ_status=="Employed", "Employed", ifelse(child_adult$employ_status=="Unemployed", "Unemployed", ifelse(is.na(child_adult$employ_status), NA_character_, "Other")))

watersource_model <- stan_glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id),
                               data = child_adult, 
                               family = "binomial", seed = 12) 

mysum <- summary(watersource_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

effects_mat <- data.frame("Outcome" = rep("Child drinks bottled water", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

#For getting tested:
tested_model <- stan_glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial", seed = 13)

mysum <- summary(tested_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])

effects_mat <- rbind(effects_mat, subdat)

#For having elevated BLLs (restricting to children who were screened):
bll_model <- stan_glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = filter(child_adult, gettested=="Yes"), family = "binomial", seed = 14) 

mysum <- summary(bll_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Elevated BLLs", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])

effects_mat <- rbind(effects_mat, subdat)

#For having rashes:
rash_model <- stan_glmer(rash ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested  + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 15)

mysum <- summary(rash_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Rashes", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat <- rbind(effects_mat, subdat)

#For having hair loss
hair_model <- stan_glmer(hair ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 16) 

mysum <- summary(hair_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Hair loss", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat <- rbind(effects_mat, subdat)

#For having learning delays:
learn_model <- stan_glmer(learn ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 17)

mysum <- summary(learn_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Learning delays", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat <- rbind(effects_mat, subdat)

#For having hyperactivity:
hyper_model <- stan_glmer(hyper ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 18)

mysum <- summary(hyper_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Hyperactivity", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat <- rbind(effects_mat, subdat)

#For having irritability:
irr_model <- stan_glmer(irritable ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 19)

mysum <- summary(irr_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Irritability", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat <- rbind(effects_mat, subdat)

#For overall symptoms:
overall_model <- stan_lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, seed = 20)

mysum <- summary(overall_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Total Symptoms", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat <- rbind(effects_mat, subdat)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

effects_mat$lower <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Lower,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Lower)
)

effects_mat$upper <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Upper,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Upper)
)

effects_mat$estimate <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate)
)

effects_mat$label <- paste0(round(effects_mat$estimate, digits=1), " (", round(effects_mat$lower, digits = 1), ", ", round(effects_mat$upper, digits = 1), ")")

pretty_effects <- dplyr::select(effects_mat, Outcome, Variable, label)
rownames(pretty_effects) <- NULL

kable(pretty_effects, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)"))
```

## Multivariable modeling results (Cauchy priors for additional regularization)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#For water source:
child_adult$water_exaggeratedbinary <- as.numeric(child_adult$water_exaggerated=="Agree" | child_adult$water_exaggerated=="Strongly Agree")
child_adult$pubben <- ifelse(child_adult$public_benefits=="Yes", 1, ifelse(is.na(child_adult$public_benefits), NA_real_, 0))
child_adult$bottledwater <- ifelse(child_adult$watersource=="Bottled water", 1, ifelse(is.na(child_adult$watersource), NA_real_, 0))
child_adult$employcollapse <- ifelse(child_adult$employ_status=="Employed", "Employed", ifelse(child_adult$employ_status=="Unemployed", "Unemployed", ifelse(is.na(child_adult$employ_status), NA_character_, "Other")))

watersource_model2 <- stan_glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id),
                               data = child_adult, 
                               family = "binomial", seed = 21,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE)) 

mysum <- summary(watersource_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

effects_mat2 <- data.frame("Outcome" = rep("Child drinks bottled water", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

#For getting tested:
tested_model2 <- stan_glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial", seed = 22,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(tested_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having elevated BLLs (restricting to children who got screened):
bll_model2 <- stan_glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = filter(child_adult, gettested=="Yes"), family = "binomial", seed = 23,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE)) 

mysum <- summary(bll_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Elevated BLLs", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having rashes:
rash_model2 <- stan_glmer(rash ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested  + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 24,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(rash_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Rashes", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having hair loss
hair_model2 <- stan_glmer(hair ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 25,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE)) 

mysum <- summary(hair_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Hair loss", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having learning delays:
learn_model2 <- stan_glmer(learn ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 26,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(learn_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Learning delays", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having hyperactivity:
hyper_model2 <- stan_glmer(hyper ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 27,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(hyper_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Hyperactivity", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having irritability:
irr_model2 <- stan_glmer(irritable ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 28,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(irr_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Irritability", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For overall symptoms:
overall_model2 <- stan_lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, seed = 29,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(overall_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Total Symptoms", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat2 <- rbind(effects_mat2, subdat)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

effects_mat2$lower <- case_when(
  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Lower,
  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Lower)
)

effects_mat2$upper <- case_when(
  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Upper,
  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Upper)
)

effects_mat2$estimate <- case_when(
  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Estimate,
  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Estimate)
)

effects_mat2$label <- paste0(round(effects_mat2$estimate, digits=1), " (", round(effects_mat2$lower, digits = 1), ", ", round(effects_mat2$upper, digits = 1), ")")

pretty_effects2 <- dplyr::select(effects_mat2, Outcome, Variable, label)
rownames(pretty_effects2) <- NULL

kable(pretty_effects2, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)"))
```
